Title

### 2013-02-08 inc/gun/gun_design.tex
added aligner picture
added short titles for the remaining figures

\begin{figure}
  \centering
  \centerline{\includegraphics{cathode.jpg} \includegraphics{anode.jpg}}
  \caption{
    Pictured are the cathode (left) and anode (right) of the accelerator built at UIC from a design by Togawa \protect\textit{et al.} \protect\cite{togawa_ceb6_2007}.
    The photocathode is visible in the cathode Wehnelt aperture.
    The anode is viewed as installed in the column, through the opened port normally occupied by the cathode and high voltage feedthrough.
    The white material seen in both images helps to prevent electrical arcing under high voltage.
  }
  \label{fig:togawa-pic}
\end{figure}

@@

\begin{figure}
  \centering
  \input{gunfield}
  \caption{
    Schematic of the employed Togawa inspired cathode ($-V$) and anode (0V) pair.
    The emission source is inserted behind the cathode Wehnelt.
    Also shown are simulated equipotential lines generated by FEM modeling.
    The separation of the cathode and anode is adjustable to allow a greater range of input laser angles if needed. 
  }
  \label{fig:gun-field}
\end{figure}

@@

>>>>

\begin{figure}
  \centering
  \centerline{\includegraphics{cathode.jpg} \includegraphics{anode.jpg}}
  \caption[Pictures of the employed Togawa-inspired custom cathode-anode pair]{
    Pictured are the cathode (left) and anode (right) of the accelerator built at UIC from a design by Togawa \protect\textit{et al.} \protect\cite{togawa_ceb6_2007}.
    The photocathode is visible in the cathode Wehnelt aperture.
    The anode is viewed as installed in the column, through the opened port normally occupied by the cathode and high voltage feedthrough.
    The white material seen in both images helps to prevent electrical arcing under high voltage.
  }
  \label{fig:togawa-pic}
\end{figure}

@@

\begin{figure}
  \centering
  \input{gunfield}
  \caption[Schematic of the employed Togawa-inspired custom cathode-anode pair]{
    Schematic of the employed Togawa-inspired cathode ($-V$) and anode (0V) pair.
    The emission source is inserted behind the cathode Wehnelt.
    Also shown are simulated equipotential lines generated by FEM modeling.
    The separation of the cathode and anode is adjustable to allow a greater range of input laser angles if needed. 
  }
  \label{fig:gun-field}
\end{figure}

@@

\begin{figure}
  \centering
  \includegraphics{aligner.jpg}
  \caption[Picture of the high-voltage side of the prototype UEM]{
    The high voltage passthrough (left) is mounted on the main chamber (right) by a ``port aligner'' which has been modified to allow coarse alignment of the cathode (mounted to the high voltage) and anode (mounted in the chamber).
  }
  \label{fig:aligner-pic}
\end{figure}

### 2013-02-08 inc/gun/gun_model.tex
began describing the Togawa gun
more gun design
added short titles for the remaining figures

\subsection{Acceleration Region}

@@

\begin{figure}
  \centerline{
    \subfloat[][]{
      \label{fig:field_on_axis}
      \input{onaxis}
    }
    \subfloat[][]{
      \label{fig:tanh_sharpness}
      \input{sharpness}
    }
  }
  \caption{
    An example of a tahn form acceleration region (overall length 6.35mm) for three different ``sharpness'' values.
    The square data points in \protect\subref{fig:field_on_axis} represent the on-axis electric field data from FEM simulations, see Section \ref{sec:gun_design}.
    The colored electric fields in \protect\subref{fig:field_on_axis} correspond to the pulse width (solid) and length (dashed) in \protect\subref{fig:tanh_sharpness}.
  }
  \label{fig:laser-cavity}
\end{figure}

\ref{fig:laser-cavity} shows an example acceleration region for three values of the ``sharpness'' $s$.
What is clear from this figure is that the dynamics are not highly coupled to the value of this hard-to-quantify parameter.
For all values of $s$ the divergence of the beam is equal (thought the size may vary slightly).
Interestingly the length of the pulse is stabilized on exiting the anode, coming very nearly to a constant length (not expanding nor contracting).
This effect is due to the slower electrons remaining in the cavity longer and thus receiving an additional kick, as described in \cite{oudheusden_electron_2007}.

>>>>

\subsection{Acceleration Region} \label{sec:gun_model}

@@

\begin{figure}
  \centerline{
    \subfloat[][]{
      \label{fig:field_on_axis}
      \input{onaxis}
    }
    \subfloat[][]{
      \label{fig:tanh_sharpness}
      \input{sharpness}
    }
  }
  \caption[An example of a tahn form acceleration region for three different ``sharpness'' values]{
    An example of a tahn form acceleration region (overall length 6.35mm) for three different ``sharpness'' values.
    The square data points in \protect\subref{fig:field_on_axis} represent the on-axis electric field data from FEM simulations, see Section \ref{sec:gun_design}.
    The colored electric fields in \protect\subref{fig:field_on_axis} correspond to the pulse width (solid) and length (dashed) in \protect\subref{fig:tanh_sharpness}.
  }
  \label{fig:gun-sharpness}
\end{figure}

\ref{fig:gun-sharpness} shows an example acceleration region for three values of the ``sharpness'' $s$.
What is clear from this figure is that the dynamics are not highly coupled to the value of this hard-to-quantify parameter.
For all values of $s$ the divergence of the beam is equal (thought the size may vary slightly).
Interestingly the length of the pulse is stabilized on exiting the anode, coming very nearly to a constant length (not expanding nor contracting).
This effect is due to the slower electrons remaining in the cavity longer and thus receiving an additional kick, as described in \cite{oudheusden_electron_2007}.

### 2013-02-08 inc/laser/laser.tex
added short titles for the remaining figures

\begin{figure}
  \subfloat[][]{
    \label{fig:crystal_geo}
    \input{crystal_geo}
  }
  \subfloat[][]{
    \label{fig:crystal_coating}
    \includegraphics{coating.jpg}
  }
  \caption{
    \protect\subref{fig:crystal_geo} Top view of the 3x3x10mm AR coated Yb:KGW laser crystal showing the crystal cut, the direction of propagation of p-polarized laser radiation at 1040nm, and the $x$ (tangential) and $y$ (saggital) directions (in blue) employed in the thermal analysis;
    \protect\subref{fig:crystal_coating} Calculated reflectivity of the 193nm \ce{SiO2} AR coating as a function of incidence angle for $p$-polarized 1040nm laser radiation (solid line) and $s$-polarized 980nm pump radiation (dashed line).
  }
  \label{fig:crystal}
\end{figure}

@@

\begin{figure}
  \centering
  \includegraphics{thermal.jpg}
  \caption{
    Analytical evaluation of the temperature distribution $T(x,y)$ due to the Gaussian/super-Gaussian heat source $Q(x,y)$ in the (a) horizontal ($y=0$) and (b) vertical ($x=0$) directions: $Q(x,y)$ - red-brown line; $T(x,y)$ - black line; parabolic approximation to $T(x,y)$ - dashed black line; representative TEM$_{00}$ laser field modes - solid green.
  }
  \label{fig:laser-thermal}
\end{figure}

@@

\begin{figure}
  \centering
  \subfloat[][]{
    \label{fig:laser_schematic}
    \input{schematic}
  }
  \\
  \subfloat[][]{
    \label{fig:laser_stability}
    \includegraphics{stability.jpg}
  }
  \caption{
    \protect\subref{fig:laser_schematic} Schematic of the femtosecond TLS Yb:KGW oscillator (LD = laser diode, OC = output coupler, SBR = saturable Bragg reflector).
    \protect\subref{fig:laser_stability} Laser mode size in the center of the Yb:KGW gain medium ($w$) as a function of the strength of the lensing ($1/f$) in the gain medium (thermal and Kerr) obtained from a resonator stability analysis with $z \approx 42$cm for both the tangential ($x$, red line) and saggital ($y$, dashed black line) directions.
    The 0.2mm (HW1/eM) vertical super-Gaussian pump spot size is indicated by the horizontal line.
  }
  \label{fig:laser-cavity}
\end{figure}

@@

\begin{figure}
  \centering
  \includegraphics{profile.jpg}
  \caption{
Second harmonic autocorrelation measurements and output spectra of the ML Yb:KGW laser; (a) the 250fs laser pulse duration (and fit assuming a sech$^2$ pulse shape) for the cavity depicted in \protect\ref{fig:laser-cavity}\protect\subref{fig:laser_schematic} at an output power of 3.5W, (b) the 347fs pulse duration (and fit assuming a sech$^2$ pulse shape) obtained with an additional -5600fs$^2$ of round-trip GVD at an output power of 5W, (c) the 4.7nm full-width half maximum spectrum associated with the 250fs ML pulse of (a), and (d) spectral output for the ML resonator of \protect\ref{fig:laser-cavity}\protect\subref{fig:laser_schematic} at a laser power of 3.7W.
  }
  \label{fig:laser-profile}
\end{figure}

@@

\begin{figure}
  \centering
  \includegraphics{performance.jpg}
  \caption{
Performance of the diode-pumped, TLS, Yb:KGW laser (in the cavity configuration of \protect\ref{fig:laser-cavity}\protect\subref{fig:laser_schematic} ) as a function of applied diode current: continuous-wave (CW) output power (black squares); mode locked (ML) output power (red circles); frequency doubled power (green triangles); and second harmonic generation (SHG) efficiency (line).
  }
  \label{fig:laser-performance}
\end{figure}

>>>>

\begin{figure}
  \subfloat[][]{
    \label{fig:crystal_geo}
    \input{crystal_geo}
  }
  \subfloat[][]{
    \label{fig:crystal_coating}
    \includegraphics{coating.jpg}
  }
  \caption[Laser crystal and anti-reflection coating]{
    \protect\subref{fig:crystal_geo} Top view of the 3x3x10mm AR coated Yb:KGW laser crystal showing the crystal cut, the direction of propagation of p-polarized laser radiation at 1040nm, and the $x$ (tangential) and $y$ (saggital) directions (in blue) employed in the thermal analysis;
    \protect\subref{fig:crystal_coating} Calculated reflectivity of the 193nm \ce{SiO2} AR coating as a function of incidence angle for $p$-polarized 1040nm laser radiation (solid line) and $s$-polarized 980nm pump radiation (dashed line).
  }
  \label{fig:crystal}
\end{figure}

@@

\begin{figure}
  \centering
  \includegraphics{thermal.jpg}
  \caption[Thermal profile and thermal lens shaping of KGW crystal pumping]{
    Analytical evaluation of the temperature distribution $T(x,y)$ due to the Gaussian/super-Gaussian heat source $Q(x,y)$ in the (a) horizontal ($y=0$) and (b) vertical ($x=0$) directions: $Q(x,y)$ - red-brown line; $T(x,y)$ - black line; parabolic approximation to $T(x,y)$ - dashed black line; representative TEM$_{00}$ laser field modes - solid green.
  }
  \label{fig:laser-thermal}
\end{figure}

@@

\begin{figure}
  \centering
  \subfloat[][]{
    \label{fig:laser_schematic}
    \input{schematic}
  }
  \\
  \subfloat[][]{
    \label{fig:laser_stability}
    \includegraphics{stability.jpg}
  }
  \caption[Schematic and stability plot of employed Yb:KGW ultrafast laser]{
    \protect\subref{fig:laser_schematic} Schematic of the femtosecond TLS Yb:KGW oscillator (LD = laser diode, OC = output coupler, SBR = saturable Bragg reflector).
    \protect\subref{fig:laser_stability} Laser mode size in the center of the Yb:KGW gain medium ($w$) as a function of the strength of the lensing ($1/f$) in the gain medium (thermal and Kerr) obtained from a resonator stability analysis with $z \approx 42$cm for both the tangential ($x$, red line) and saggital ($y$, dashed black line) directions.
    The 0.2mm (HW1/eM) vertical super-Gaussian pump spot size is indicated by the horizontal line.
  }
  \label{fig:laser-cavity}
\end{figure}

@@

\begin{figure}
  \centering
  \includegraphics{profile.jpg}
  \caption[Autocorrelation measurements of employed ultrafast laser's pulse duration]{
Second harmonic autocorrelation measurements and output spectra of the ML Yb:KGW laser; (a) the 250fs laser pulse duration (and fit assuming a sech$^2$ pulse shape) for the cavity depicted in \protect\ref{fig:laser-cavity}\protect\subref{fig:laser_schematic} at an output power of 3.5W, (b) the 347fs pulse duration (and fit assuming a sech$^2$ pulse shape) obtained with an additional -5600fs$^2$ of round-trip GVD at an output power of 5W, (c) the 4.7nm full-width half maximum spectrum associated with the 250fs ML pulse of (a), and (d) spectral output for the ML resonator of \protect\ref{fig:laser-cavity}\protect\subref{fig:laser_schematic} at a laser power of 3.7W.
  }
  \label{fig:laser-profile}
\end{figure}

@@

\begin{figure}
  \centering
  \includegraphics{performance.jpg}
  \caption[Power measuments of employed ultrast laser]{
Performance of the diode-pumped, TLS, Yb:KGW laser (in the cavity configuration of \protect\ref{fig:laser-cavity}\protect\subref{fig:laser_schematic} ) as a function of applied diode current: continuous-wave (CW) output power (black squares); mode locked (ML) output power (red circles); frequency doubled power (green triangles); and second harmonic generation (SHG) efficiency (line).
  }
  \label{fig:laser-performance}
\end{figure}

### 2013-02-08 inc/model_results/spacecharge/spacecharge.tex
added spacecharge plot (beam size vs number of electrons)
added short titles for the remaining figures

>>>>

\begin{figure}
  \centering
  \begin{tikzpicture}
    \input{spacecharge_data}
  \end{tikzpicture}
  \caption[Free-space pulse evolution vs initial shape]{
    The final HW1/eM width (solid) and length (dashed) of similar initial size pulses for different number of electrons in the pulse.
    The pulse is generated by 1 mm (HW1/eM) width 1 ps laser pulses, then traverse a 20mm acceleration region and a 15cm drift region.
  }
  \label{fig:spacecharge}
\end{figure}
